Recalibrating Gravitational Wave Phenomenological Waveform Model

### 2024-02-01 src/tex/ms.tex
slight text change

\corr{We note that the parameter space we use is restricted to $q\leq8$, while waveforms 
of $q=18$ are used in the original calibration trial. Also, we have directly used NR 
waveforms instead of hybridized SEOB-NR waveforms for training and validation purposes. 
These choices put the original IMRPhenomD result at a disadvantage, as both the parameter 
space and frequency range are restricted. We tested our result by training the model 
using a set of training waveforms of the same intrinsic parameters, but with BAM waveforms 
replaced with SEOBNR waveforms. We can see the result in Fig.~\ref{fig:q14818}, where the 
mismatch median decreases by about $8\%$, This mismatch improvement mainly concerns the 
stitching problem discussed before. Nevertheless, it is known that IMRPhenomD has a large 
inaccuracy in the large mass-ratio regime, and is rarely used in this region of parameter 
space. Hence, we focus on showing AD with gradient descent, as a general and robust method, 
can be used to further optimize GW waveform models with arbitrary sets of training 
waveforms used.}

>>>>

\corr{We note that the parameter space we use is restricted to $q\leq8$, while waveforms 
of $q=18$ are used in the original calibration trial. Also, we have directly used NR 
waveforms instead of hybridized SEOB-NR waveforms for training and validation purposes. 
These choices put the original IMRPhenomD result at a disadvantage, as both the parameter 
space and frequency range are restricted. We tested our result by training the model 
using a set of training waveforms of the same intrinsic parameters, but with BAM waveforms 
replaced with SEOBNR waveforms. We can see the result in Fig.~\ref{fig:q14818}, where the 
mismatch median decreases by about $8\%$. Nevertheless, it is known that IMRPhenomD has a large 
inaccuracy in the large mass-ratio regime, and is rarely used in this region of parameter 
space. Hence, we focus on showing that AD with gradient descent, as a general and robust method, 
can be used to further optimize GW waveform models with arbitrary sets of training 
waveforms used.}
